
# Clean up and load libraries
```{r}
rm(list = ls())
options(scipen = 4)
library(QCA)
library(tidyverse)
library(lubridate)
library(pcse)
```

# Data importing & cleaning

## Load turnout dataset
```{r}
ds <- read.csv("dataset.csv")
```

## Load parlgov election view
```{r}
# Country-level aggregates
pg <- left_join(
  read.csv("pg_elec.csv") %>% select(election_id, country_name, country_name_short, election_type, election_date),
  read.csv("pg_elec_calc.csv") %>% select(election_id, turnout)
) %>% unique() %>% mutate(Year = year(ymd(election_date)))

# Individual party results
pg.party <- 
  read.csv("pg_elec.csv") %>% 
  select(election_id, country_name, election_type, election_date, party_id, vote_share) %>%
  mutate(Year = year(ymd(election_date))) %>%
  filter(election_type == "ep")
```

## Load PopuList
```{r echo=FALSE, warning=FALSE}
populist <- read.csv("populist_v2.csv") %>% mutate(party_id = parlgov_id)
```

## Load data on national parliamentary terms
```{r}
terms <- read.csv("terms.csv")
```

## Load OECD employment data
```{r}
agr.oecd <- left_join(
  read.csv("oecd_sector.csv") %>% select(Code = LOCATION, Year = TIME, Agr = Value),
  read.csv("oecd_lf.csv") %>% select(Code = LOCATION, Year = TIME, LF = Value)
) %>% left_join(
  read.csv("oecd_codes.csv")
) %>%
  mutate(AgrShare = Agr / LF) %>%
  filter(!is.na(Country)) %>%
  select(Country, Year, AgrShare)
```

## Load ILO employment data
```{r}
agr.ilostat <- read.csv("ilostat.csv") %>% 
  select(
    Country = ref_area.label,
    Year = time,
    Var = classif1.label,
    Val = obs_value)
agr.ilostat <- left_join(
  agr.ilostat %>% 
    filter(Var == "Economic activity (Aggregate): Agriculture") %>% 
    select(Country, Year, Agr = Val),
  agr.ilostat %>%
    filter(Var == "Economic activity (Aggregate): Total") %>%
    select(Country, Year, Total = Val)
) %>%
  mutate(AgrShare = Agr / Total)
```

## Merge employment datasets
```{r}
agr <- full_join(
  agr.oecd %>% select(Country, Year, AgrShareOecd = AgrShare),
  agr.ilostat %>% select(Country, Year, AgrShareIlostat = AgrShare)
) %>% mutate(AgrShare = rowMeans(cbind(AgrShareOecd, AgrShareIlostat), na.rm = T))
```

## Calculate eurosceptic vote shares
```{r}
euscep <- 
  left_join(pg.party, populist, by = "party_id") %>%
  filter((eurosceptic_startnobl <= Year & eurosceptic_endnobl > Year)) %>%
  rename(Country = country_name.x) %>%
  group_by(Country, Year) %>%
  summarise(EuroscepticVoteShare = sum(vote_share) / 100)
```

## Merge all datasets together
```{r}
ds <- ds %>% left_join(
  pg %>% 
    filter(election_type == "ep") %>% 
    select(Country = country_name, CountryShort = country_name_short, Year, TurnoutPG = turnout, Date = election_date)
) %>%   
  left_join(terms) %>%
  left_join(agr %>% select(Country, Year, AgrShare)) %>%
  left_join(euscep) %>%
  mutate(EuroscepticVoteShare = replace(EuroscepticVoteShare, is.na(EuroscepticVoteShare), 0)) %>%
  mutate(label = paste(CountryShort, Year, sep = "")) %>%
  drop_na()
```

## Derive national election variables
```{r}
last_national_election <- function(country, date) {
  res <- pg %>% filter(election_type == "parliament" & country_name == country & election_date < date)
  max(res$election_date)
}

ds <- ds %>% mutate(LastNational = mapply(last_national_election, Country, Date))
ds <- ds %>% mutate(Cycle = (interval(LastNational, Date) %/% days(1)) / (365.25 * Term))
ds <- ds %>% mutate(CycleM = interval(LastNational, Date) %/% months(1))
ds <- left_join(ds, pg %>% filter(election_type == "parliament") %>% select(Country = country_name, LastNational = election_date, LastNationalTurnout = turnout))
```

## Calculate eurogap
```{r}
ds <- ds %>% mutate(Eurogap = LastNationalTurnout - Turnout)
```

## Define base years

For regular EU-wide elections, this refers to the respective election year.
For irregular elections conducted on accession, this refers to the previous regular EU-wide election year.
```{r}
# Decide which calibration to use based on election year
ds <- ds %>% mutate(BaseYear = case_when(
  Year <  1984               ~ 1979,
  Year >= 1984 & Year < 1989 ~ 1984,
  Year >= 1989 & Year < 1994 ~ 1989,
  Year >= 1994 & Year < 1999 ~ 1994,
  Year >= 1999 & Year < 2004 ~ 1999,
  Year >= 2004 & Year < 2009 ~ 2004,
  Year >= 2009 & Year < 2014 ~ 2009,
  Year >= 2014 & Year < 2019 ~ 2014,
  Year >= 2019               ~ 2019))
```

## Label cases

```{r}
rownames(ds) <- ds$label
```

# Definition and calibration of sets for QCA

## T = Turnout (Outcome)
We want to calibrate with reference to election year, to focus on cross-country differences.
Post-accession elections should be calibrated based on the previous EU-wide election year.
```{r}
# Function to compute turnout quantiles for a given election year
qT <- function (year) {
  q <- quantile(filter(ds, Year == year)$Turnout, probs = c(0.2, 0.5, 0.8))
  q[2] <- q[2] - .001 # Slightly offset median to avoid perfect .5 membership scores
  q
}
# Calibrations with reference to all EU-wide election years
ds$T1979 <- calibrate(ds$Turnout, thresholds = qT(1979))
ds$T1984 <- calibrate(ds$Turnout, thresholds = qT(1984))
ds$T1989 <- calibrate(ds$Turnout, thresholds = qT(1989))
ds$T1994 <- calibrate(ds$Turnout, thresholds = qT(1994))
ds$T1999 <- calibrate(ds$Turnout, thresholds = qT(1999))
ds$T2004 <- calibrate(ds$Turnout, thresholds = qT(1994))
ds$T2009 <- calibrate(ds$Turnout, thresholds = qT(2009))
ds$T2014 <- calibrate(ds$Turnout, thresholds = qT(2014))
ds$T2019 <- calibrate(ds$Turnout, thresholds = qT(2019))
# Decide which calibration to use based on election year
ds <- ds %>% mutate(T = case_when(
  BaseYear == 1979 ~ T1979,
  BaseYear == 1984 ~ T1984,
  BaseYear == 1989 ~ T1989,
  BaseYear == 1994 ~ T1994,
  BaseYear == 1999 ~ T1999,
  BaseYear == 2004 ~ T2004,
  BaseYear == 2009 ~ T2009,
  BaseYear == 2014 ~ T2014,
  BaseYear == 2019 ~ T2019))
plot(ds$Turnout, ds$T)
```

## G = Eurogap (Outcome)
```{r}
ds$G = calibrate(ds$Eurogap, thresholds = c(10,20,30))
plot(ds$Eurogap, ds$G)
```


## C = Compulsory Voting (Crisp Condition)
```{r}
ds$C <- 0
ds$C[ds$Country %in% c("Belgium", "Greece", "Luxembourg")] <- 1
ds$C[ds$Country == "Italy" & ds$Year <= 1993] <- 1
ds$C[ds$Country == "Cyprus" & ds$Year <= 2017] <- 1
ds$C[ds$Country == "Bulgaria" & ds$Year >= 2016] <- 1
```

## H = Institution host country? (Crisp Condition)
```{r}
ds$H <- 0
ds$H[ds$Country %in% c("Belgium", "Luxembourg", "France")] <- 1
ds$H[ds$Country == "Germany" & ds$Year >= 1999] <- 1
```

## N = Turnout at previous national (Fuzzy Condition)
```{r}
qN <- quantile(ds$LastNationalTurnout, probs = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9))
qN
```

```{r}
ds$N <- ds$LastNationalTurnout %>% calibrate(thresholds = c(qN[2], qN[5] + 1, qN[8]))
plot(ds$LastNationalTurnout, ds$N)
```

## E = Time in national election cycle (Fuzzy Condition)
```{r}
ds$E <- ds$Cycle %>% calibrate(thresholds = c(0.25, 0.5, 0.75))
plot(ds$Cycle, ds$E)
```

## A = Agrarian economy? (Fuzzy Condition)
```{r}
qA <- quantile(ds$AgrShare, probs = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9))
qA
```

```{r}
ds$A <- ds$AgrShare %>% calibrate(thresholds = c(qA[2], qA[5] + .000001, qA[8]))
plot(ds$AgrShare, ds$A)
```

## L = Lead candidates from the country? (Crisp Condition)
```{r}
ds <- ds %>% mutate(L = LeadCandidate)
```

## S = Prominent euroscepticism? (Fuzzy condition)
```{r}
ds$S <- ds$EuroscepticVoteShare %>% calibrate(thresholds = c(0, 0.1, 0.3))
plot(ds$EuroscepticVoteShare, ds$S)
```

# OLS Regressions
```{r}
ds.reg <- ds %>% mutate(
  AgrShare = AgrShare * 100,
  Country = as.factor(Country),
  Year_ = as.factor(Year))
```

## Turnout

### Model 4 (Flickinger & Studlar 2007)
```{r}
reg1 <- lm(
  data = ds.reg,
  formula = Turnout ~ C + CycleM + LastNationalTurnout + H + AgrShare + Year_)
reg1.pcse <- pcse(
  object = reg1,
  groupN = ds.reg$Country,
  groupT = ds.reg$Year,
  pairwise = TRUE)
summary(reg1)
summary(reg1.pcse)
```

### Model 4 + Euroscepticism & Lead Candidates
```{r}
reg2 <- lm(
  data = ds.reg,
  formula = Turnout ~ C + CycleM + LastNationalTurnout + H + AgrShare + LeadCandidate + EuroscepticVoteShare + Year_)
reg2.pcse <- pcse(
  object = reg2,
  groupN = ds.reg$Country, 
  groupT = ds.reg$Year, 
  pairwise = TRUE)
summary(reg2)
summary(reg2.pcse)
```

# Model comparison
```{r}
anova(reg1, reg2)
```

## Eurogap

### Model 4
```{r}
reg3 <- lm(
  data = ds.reg,
  formula = Eurogap ~ C + CycleM + H + AgrShare + Year_)
reg3.pcse <- pcse(
  object = reg3,
  groupN = ds.reg$Country,
  groupT = ds.reg$Year,
  pairwise = TRUE)
summary(reg3)
summary(reg3.pcse)
```

### Model 4 + Euroscepticism & Lead Candidates
```{r}
reg4 <- lm(
  data = ds.reg,
  formula = Eurogap ~ C + CycleM + H + AgrShare + LeadCandidate + EuroscepticVoteShare + Year_)
reg4.pcse <- pcse(
  object = reg4,
  groupN = ds.reg$Country, 
  groupT = ds.reg$Year, 
  pairwise = TRUE)
summary(reg4)
summary(reg4.pcse)
```

# Qualitative Comparative Analysis

## Turnout within base year

### Select variables and directional expectations
```{r}
qca1.ds <- ds %>% select(T, C, H, N, E, A, S)
qca1.direxp.high = "1,1,1,1,1,0"
qca1.direxp.low = "0,0,0,0,0,1"
qca1.cutoff = ".8"
qca1.method = "QMC"
```

### Positive outcome (high turnout)

#### truth table
```{r}
qca1.high.tt <- truthTable(
  data = qca1.ds,
  outcome = "T",
  show.cases = TRUE,
  incl.cut = qca1.cutoff)
qca1.high.tt
```

#### Conservative solution
```{r}
qca1.high.conserv <- minimize(qca1.high.tt, details = TRUE, method = qca1.method)
qca1.high.conserv
```

#### Parsimonious solution
```{r}
qca1.high.parsim <- minimize(qca1.high.tt, include = "?", details = TRUE, method = qca1.method)
qca1.high.parsim
```

#### Intermediate solution
```{r}
qca1.high.interm <- minimize(qca1.high.tt, include = "?", dir.exp = qca1.direxp.high, details = TRUE, method = qca1.method)
qca1.high.interm
```

### Negative outcome (low turnout)

#### Truth table
```{r}
qca1.low.tt <- truthTable(
  data = qca1.ds, 
  outcome = "~T", 
  show.cases = TRUE,
  incl.cut = qca1.cutoff)
qca1.low.tt
```

#### Conservative solution
```{r}
qca1.low.conserv <- minimize(qca1.low.tt, details = TRUE, method = qca1.method)
qca1.low.conserv
```

#### Parsimonious solution
```{r}
qca1.low.parsim <- minimize(qca1.low.tt, include = "?", details = TRUE, method = qca1.method)
qca1.low.parsim
```

#### Intermediate solution
```{r}
qca1.low.interm <- minimize(qca1.low.tt, include = "?", dir.exp = qca1.direxp.low, details = TRUE, method = qca1.method)
qca1.low.interm
```

## Eurogap

### Select variables and directional expectations
```{r}
qca2.ds <- ds %>% arrange(Country) %>% select(C, H, E, A, S, G)
qca2.direxp.high = "0,0,0,0,1"
qca2.direxp.low = "1,1,1,1,0"
qca2.cutoff = ".8"
qca2.method = "QMC"
```

### Positive outcome (high turnout)

#### truth table
```{r}
qca2.high.tt <- truthTable(
  data = qca2.ds,
  outcome = "G",
  show.cases = TRUE,
  incl.cut = qca2.cutoff)
qca2.high.tt
```

#### Conservative solution
```{r}
qca2.high.conserv <- minimize(qca2.high.tt, details = TRUE, method = qca2.method)
qca2.high.conserv
```

#### Parsimonious solution
```{r}
qca2.high.parsim <- minimize(qca2.high.tt, include = "?", details = TRUE, method = qca2.method)
qca2.high.parsim
```

#### Intermediate solution
```{r}
qca2.high.interm <- minimize(qca2.high.tt, include = "?", dir.exp = qca2.direxp.high, details = TRUE, method = qca2.method)
qca2.high.interm
```

### Negative outcome (low turnout)

#### Truth table
```{r}
qca2.low.tt <- truthTable(
  data = qca2.ds, 
  outcome = "~G", 
  show.cases = TRUE,
  incl.cut = qca2.cutoff)
qca2.low.tt
```

#### Conservative solution
```{r}
qca2.low.conserv <- minimize(qca2.low.tt, details = TRUE, method = qca2.method)
qca2.low.conserv
```

#### Parsimonious solution
```{r}
qca2.low.parsim <- minimize(qca2.low.tt, include = "?", details = TRUE, method = qca2.method)
qca2.low.parsim
```

#### Intermediate solution
```{r}
qca2.low.interm <- minimize(qca2.low.tt, include = "?", dir.exp = qca2.direxp.low, details = TRUE, method = qca2.method)
qca2.low.interm
```

# Export results
```{r}
save.image(file = "results.RData")
```
